\LARGE \bf Analysis of the effectiveness of recursive networks in the classification task

### 2019-06-12 paper/main.tex
paper: hilbert curve plot finished
paper: caption of hilbert curve image expanded

\begin{figure}
	\centering
	\begin{tikzpicture}
	\draw (0,0) node[below] {1}
	-- (0,2.1) node[above] {2} 
	-- (2.1,2.1) node[above] {3} 
	-- (2.1,0) node[below] {4};
	\draw (0,3.0) node[above] {1} 
	-- (0.66,3.0) node[below] {2} 
	-- (1.32,3.0) node[above] {3} 
	-- (2,3.0) node[below] {4};
	\draw (3,0) node[below] {1} 
	-- (3+0.7,0) node[below] {2} 
	-- (3+0.7,0+0.7) 
	-- (3,0+0.7) 
	-- (3,0+0.7+0.7) 
	-- (3,0+0.7+0.7+0.7) 
	-- (3+0.7,0+0.7+0.7+0.7) 
	-- (3+0.7,0+0.7+0.7) 
	-- (3+0.7+0.7,0+0.7+0.7) 
	-- (3+0.7+0.7,0+0.7+0.7+0.7) 
	-- (3+0.7+0.7+0.7,0+0.7+0.7+0.7) 
	-- (3+0.7+0.7+0.7,0+0.7+0.7)  
	-- (3+0.7+0.7+0.7,0+0.7) 
	-- (3+0.7+0.7,0+0.7) 
	-- (3+0.7+0.7,0) 
	-- (3+0.7+0.7+0.7,0);
	\draw (3,3) node[above] {1}
	-- (5.1,3) node[above] {2};
	\draw (6.25,0) 
	-- (6.25,0+0.3) 
	-- (6.25+0.3,0+0.3)
	-- (6.25+0.3,0)
	-- (6.25+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3,0+0.3+0.3)
	-- (6.25,0+0.3+0.3)
	-- (6.25,0+0.3+0.3+0.3)
	-- (6.25,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0)
	;
	\end{tikzpicture}
\caption{First 3 elements of sequence creating Hilbert Curve.}
	\label{fig:hilbert}
\end{figure}

>>>>

\begin{figure}
	\centering
	\begin{tikzpicture}
	\draw (0,0) node[below] {\tiny 1}
	-- (0,2.1) node[above] {\tiny 2} 
	-- (2.1,2.1) node[above] {\tiny 3} 
	-- (2.1,0) node[below] {\tiny 4};
	\draw (0,3.0) node[above] {\tiny 1} 
	-- (0.66,3.0) node[below] {\tiny 2} 
	-- (1.32,3.0) node[above] {\tiny 3} 
	-- (2,3.0) node[below] {\tiny 4};
	\draw (3,0) node[below] {\tiny 1} 
	-- (3+0.7,0) node[below] {\tiny 2} 
	-- (3+0.7,0+0.7) node[below left] {\tiny 3}
	-- (3,0+0.7) node[below left] {\tiny 4}
	-- (3,0+0.7+0.7) node[left] {\tiny 5}
	-- (3,0+0.7+0.7+0.7) node[above left] {\tiny 6}
	-- (3+0.7,0+0.7+0.7+0.7) node[above] {\tiny 7}
	-- (3+0.7,0+0.7+0.7) node[below] {\tiny 8}
	-- (3+0.7+0.7,0+0.7+0.7) node[below] {\tiny 9}
	-- (3+0.7+0.7,0+0.7+0.7+0.7) node[above] {\tiny 10}
	-- (3+0.7+0.7+0.7,0+0.7+0.7+0.7) node[above right] {\tiny 11}
	-- (3+0.7+0.7+0.7,0+0.7+0.7) node[right] {\tiny 12}
	-- (3+0.7+0.7+0.7,0+0.7) node[below right] {\tiny 13}
	-- (3+0.7+0.7,0+0.7) node[below right] {\tiny 14}
	-- (3+0.7+0.7,0) node[below] {\tiny 15}
	-- (3+0.7+0.7+0.7,0) node[below] {\tiny 16}; 
	\draw (3,3) node[above] {\tiny 1}
	-- (3+0.14,3) node[below] {\tiny 2}
	-- (3+2*0.14,3) node[above] {\tiny 3}
	-- (3+3*0.14,3) node[below] {\tiny 4}
	-- (3+4*0.14,3) node[above] {\tiny 5}
	-- (3+5*0.14,3) node[below] {\tiny 6}
	-- (3+6*0.14,3) node[above] {\tiny 7}
	-- (3+7*0.14,3) node[below] {\tiny 8}
	-- (3+8*0.14,3) node[above] {\tiny 9}
	-- (3+9*0.14,3) node[below] {\tiny 10}
	-- (3+10*0.14,3) node[above] {\tiny 11}
	-- (3+11*0.14,3) node[below] {\tiny 12}
	-- (3+12*0.14,3) node[above] {\tiny 13}
	-- (3+13*0.14,3) node[below] {\tiny 14}
	-- (3+14*0.14,3) node[above] {\tiny 15}
	-- (3+0.7+0.7+0.7,3) node[below] {\tiny 16};
	\draw (6.25,0) node[below] {\tiny 1}
	-- (6.25,0+0.3)
	-- (6.25+0.3,0+0.3)
	-- (6.25+0.3,0)
	-- (6.25+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3,0+0.3+0.3)
	-- (6.25,0+0.3+0.3)
	-- (6.25,0+0.3+0.3+0.3)
	-- (6.25,0+0.3+0.3+0.3+0.3) %node[left] {\tiny 17}
	-- (6.25+0.3,0+0.3+0.3+0.3+0.3) %node[right] {\tiny 18}
	-- (6.25+0.3,0+0.3+0.3+0.3+0.3+0.3) %node[right] {\tiny 19}
	-- (6.25,0+0.3+0.3+0.3+0.3+0.3) %node[left] {\tiny 20}
	-- (6.25,0+0.3+0.3+0.3+0.3+0.3+0.3) %node[above left] {\tiny 21}
	-- (6.25,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3) node[above] {\tiny 22}
	-- (6.25+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3) node[above] {\tiny 27}
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0+0.3)
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,0) node[below] {\tiny 64}
	;
	\draw (6.25,3) node[above] {\tiny 1}
	-- (6.25+1*0.033,3) %node[below] {\tiny 2}
	-- (6.25+16*0.033,3) %node[below] {\tiny 17}
	-- (6.25+17*0.033,3) %node[below] {\tiny 18}
	-- (6.25+18*0.033,3) %node[below] {\tiny 19}
	-- (6.25+19*0.033,3) %node[below] {\tiny 20}
	-- (6.25+20*0.033,3) %node[below] {\tiny 21}
	-- (6.25+21*0.033,3) node[below] {\tiny 22}
	-- (6.25+26*0.033,3) node[above] {\tiny 27}
	-- (6.25+0.3+0.3+0.3+0.3+0.3+0.3+0.3,3) node[above] {\tiny 64};
	\end{tikzpicture}
\caption{First 3 elements of sequence creating Hilbert Curve. Points 2 from first curve, 6 and 7 from second curve and 22 and 27 correspond to a similar regions in an image and are mapped to close points on a line.}
	\label{fig:hilbert}
\end{figure}
